Inspect YAGMH_SFREQ

### 2024-09-18 Rmd/does_subsampling_WOR_matter.Rmd
Implement new sample size functionality. test sample size=10 haul level, length, 1999-2023. Works.

BUT, now the question is, do I subsample the samples or run the whole thing again with the different N? I think running the whole thing again is better because we further randomize the hauls chosen by re-randomize the trips and hauls. But perhaps it does not matter because on average, both sets of resampled trips/hauls should be equally representative at high enough iterations. in SWO, they subsample right after boot_length for every iteration. This means they take the same resampled hauls to subsample. I'm not sure why they do this instead of resample the hauls again. Is it just for speed optimization?

For now, I'm going to code it into the existing boot_length function and necessitate running the whole thing over again if we want to resample. One potential advantage of doing it this way is that, since the sampling rate varies wildly prior to 1999, the years for which subsampling is applied will probably not be the full data year span. Therefore, the existing yrs option in fishery_iss can be used to control years to apply subsamples to. I can consider doing it the other way in the future. Start with length. start with a fixed value, 10, just for 1999 and up I guess. Note that this cannot be applied when post_strata = "SEX" because the 20 fish target is sex-independent.

Min/max problem: In SWO, the min(.N, samples) is taken. This is done instead of max() because they only considered reducing the sampling effort. I need to decide what to do with baseISS because I want to investigate greater-than sampling rates. Perhaps have a conditional statement that conditions on > or < the median YAGMH_SFREQ for the yrs spanned.

>>>>

BUT, now the question is, do I subsample the samples or run the whole thing again with the different N? I think running the whole thing again is better because we further randomize the hauls chosen by re-randomize the trips and hauls. But perhaps it does not matter because on average, both sets of resampled trips/hauls should be equally representative at high enough iterations. in SWO, they subsample right after boot_length for every iteration. This means they take the same resampled hauls to subsample. I'm not sure why they do this instead of resample the hauls again. Is it just for speed optimization? Is there a more substantial reason?

For now, I'm going to code it into the existing boot_length function and necessitate running the whole thing over again if we want to resample. One potential advantage of doing it this way is that, since the sampling rate varies wildly prior to 1999, the years for which subsampling is desired to be applied will probably not be the full data year span. Therefore, the existing yrs option in fishery_iss can be used to control years to apply subsamples to. I can consider doing it the other way in the future. Start with length. start with a fixed value, 10, just for 1999 and up I guess. Note that this cannot be applied when post_strata = "SEX" because the 20 fish target is sex-independent.

Min/max problem: In SWO, the min(.N, samples) is taken. This is done instead of max() because they only considered reducing the sampling effort. I need to decide what to do with baseISS because I want to investigate greater-than sampling rates. I think this should be the lesser-than number in either case relative to the mean of the median YAGMH_SFREQ for the yrs spanned. Code it this way for now but continue to think about it.

### 2024-09-18 Rmd/haul_sample_size_investigation.Rmd
Implement new sample size functionality. test sample size=10 haul level, length, 1999-2023. Works.

>>>>

## Check out YAGMH_SFREQ 1999-2023 in more detail

```{r}
lfreq_data[YEAR%in%c(1999:2023),] %>% tidytable::distinct(HAUL_JOIN, .keep_all = T) %>% tidytable::select(YAGMH_SFREQ)->temp

hist(temp$YAGMH_SFREQ)
summary(temp$YAGMH_SFREQ) # 540 is max!!!

((temp$YAGMH_SFREQ>20) %>% sum)/nrow(temp)
((temp$YAGMH_SFREQ>25) %>% sum)/nrow(temp) # about 2% over 20

plot(temp$YAGMH_SFREQ[temp$YAGMH_SFREQ>25])
plot(temp$YAGMH_SFREQ[temp$YAGMH_SFREQ>25], ylim = c(20, 100))
